Designing Types for R, Empirically

### 2020-10-12 paper/main.tex
stuff

The basic building blocks of R are vectors of primitives (primitives
in R are characters (strings), integers, logicals (booleans), doubles,
complex numbers, and raw bytes).  When we say that R is {\it
  vectorized}, we mean that primitive values are {\it always} vectors.
For example, in R one might see the literal \code{2.5} and think it to
be a scalar double, but it is in actuality a unit-length vector
containing a single double.  Vectors can also be explicitly
constructed using the vector constructor \code{c(...)}, For example,
\code{c(1L, 2L, 3L)} creates a vector of three integers (in R, integer
literals are denoted by an \code{L}).  To illustrate that scalars are
vectors, in R \code{(c(2.5) == 2.5) == TRUE}.

The main object of our work is R functions, and functions in R have a
number of quirks.  Arguments can be assigned default values (which can
be arbitrary expressions!), and functions can support variable
argument lists, and functions can be called by specifying argument
names explicitly in the call.  To illustrate all of this in a single
example, consider:

>>>>

It's basic building blocks are vectors of primitives (primitives in R
are characters (or strings), integers, logicals (or booleans),
doubles, complex numbers, and raw bytes).  To say that R is vectorized
implies that primitive values are {\it always} vectors.  For example,
the literal \code{2.5} is a unit-length vector containing a single
double.  Vectors can be explicitly constructed using the constructor
\code{c(...)}, as in \code{c(1L, 2L, 3L)} which creates a vector of
three integers.

The main object of our work is functions, and R functions have a
number of quirks.  Arguments can be assigned arbitrary expressions as
default values, and functions can support variable
argument lists, and functions can be called by specifying argument
names explicitly in the call.  To illustrate all of this in a single
example, consider:
